---
title: "Belt and Road Initiative Investment Stat in MENA"
author: "Ruoqi Zhang"
date: "4/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
library(plotly)
library(ggthemes)
library(scales)
library(gt)
```

## Description of Data

American Enterprise Institute's China Global Investment Tracker (CGIT) is the only publicly available dataset recording China's global investment. It contains both BRI and non-BRI investments around the world. It also provides details of those investments, including country, participating companies, size of the investment, and the sector of the investment.

For the purpose of this research project, we are interested in BRI-related investment projects in select countries involved in BRI.

```{r data_processing}
# We use data from American Enterprise Institute's China Global Investment
# Tracker as the basis for our analysis. There are multiple sheets in the
# dataset, and we are interested in the sheet that contains data regarding
# investment as well as construction projects.

investment <- read_excel("China-Global-Investment-Tracker-2018.xlsx", sheet = "Dataset 1+2", skip = 4)

# AEI's CGIT dataset contains both BRI and non-BRI investments, reflected in its
# BRI variable. For the purpose of this project, we are only interestedin
# BRI-related investment. Therefore, we first clean the variable's names using
# janitor package, and filter BRI-related rows.

bri_investment <- investment %>% 
  clean_names() %>% 
  filter(bri == TRUE)

```

## BRI Investments in MENA

According to the dataset, there are `r count(bri_investment)` BRI-related investments internationally since the initiation of this initiative. In Arab Middle East and North America, there are `r bri_investment %>% filter(region == "Arab Middle East and North Africa") %>% count()` investment records with total aggregate value of USD `r bri_investment %>% filter(region == "Arab Middle East and North Africa") %>% summarize(sum(quantity_in_millions))` million.

```{r bri_trend, fig.height = 6, fig.width = 10}
bri_investment %>% 
  filter(country %in% c("Turkey", "Iran", "Saudi Arabia", "UAE", "Egypt", "Oman", "Qatar", "Iraq")) %>% 
  group_by(year, country) %>% 
  summarize(total_investment = sum(quantity_in_millions)) %>% 
  arrange(desc(total_investment)) %>% 
  # plot_ly(x = ~year, y = ~total_investment, color = ~country, type = 'scatter', mode = 'line')
  ggplot(aes(x = year, y = total_investment, color = country)) +
    geom_line() +
    theme_minimal() +
    scale_y_continuous(breaks = c(0, 2000, 4000, 6000, 8000),
                       labels = c("$0", "$2bn", "$4bn", "$6bn", "$8bn")) +
    labs(x = NULL,
         y = NULL,
         title = "Aggregate Value of Belt and Road Initiative Investments, in Billion USD",
         subtitle = "In Middle Eastern, North African, and West Ansian Countries, 2013 - 2018, by year",
         color = "Country",
         caption = "Source: China Global Investment Tracker/American Enterprise Institute") -> bri_investment_trend

ggsave(filename = "bri_investment_trend.png", 
       plot = bri_investment_trend,
       width = 10,
       height = 6,
       dpi = 300)

bri_investment_trend
```

```{r bri_investment_quantity}
bri_investment %>% 
  filter(region == "Arab Middle East and North Africa" | country %in% c("Turkey", "Iran", "Syria")) %>%
  group_by(country, year) %>% 
  summarize(total_investment = sum(quantity_in_millions)) %>% 
  spread(key = year, value = total_investment) %>% 
  ungroup() %>% 
  mutate_all(list(~replace_na(.,0))) %>%
  mutate(total_investment = `2013` + `2014` + `2015` + `2016` + `2017` + `2018`) %>% 
  arrange(desc(total_investment)) %>% 
  gt() %>% 
  tab_header(
    title = 'Belt and Road Initiative Investments in Middle East',
    subtitle = "Aggregate investment in million dollars, 2013-2018"
  ) %>% 
  gt(rowname_col = "country") %>% 
  tab_stubhead_label(label = "Country") %>% 
  cols_label(total_investment = "Total Investment") %>% 
  tab_source_note(source_note = "Source: China Global Investment Tracker/American Enterprise Institute") %>% 
  fmt_currency(
    columns = vars(`2013`, `2014`, `2015`, `2016`, `2017`, `2018`, total_investment),
    currency = "USD",
    decimals = 0,
    pattern = "{x} M") -> bri_investment_quantity

bri_investment_quantity
```

